\begin{abstract}
  JavaScript is one of the most popular interpreted programming languages used
  in diverse fields.
  %
  To support consistent execution environments anywhere, JavaScript engines and
  transpilers must conform to the ECMAScript language specification called
  ECMA-262.
  %
  Therefore, it is essential to maintain a \textit{conformance test} suite
  consisting of JavaScript programs with assertions that check the expected
  behaviors according to the specification.
  %
  However, it is challenging to do it automatically because of the complex
  language semantics with a highly dynamic nature and the fast-evolving language
  specification.
  %
  Prior work utilizes coverage-guided fuzzing with \textit{node/branch
  coverages} in the control-flow graph (CFG) of language specification to
  synthesize conformance tests.
  %
  Unfortunately, such simple coverage metrics cannot fully discriminate test
  programs related to different language features whose semantics are defined
  with shared abstract algorithms in the specification.
  %
  As a result, they lower the quality of the fuzzing guidance and might even
  remove meaningful test programs in the final suite.
  %
  In addition, prior work focuses on conformance checks only for engines but
  does not consider transpilers.

  %----------------------------------------%

  This paper introduces a novel \textit{feature-sensitive coverage} as a general
  extension of any coverage metrics.
  %
  It enhances the quality of the coverage-guided fuzzing by discriminating the
  covered elements with enclosing calling contexts that consist of
  \textit{language features} and \textit{intra-feature call graphs}.
  %
  In addition, we extend it to cover pair-wise combinations between different
  language features.
  %
  Then, we generalize prior work to synthesize conformance tests for both
  JavaScript engines and transpilers.
  %
  To actualize our techniques, we implemented $\tool$ by extending a
  state-of-the-art JavaScript conformance test synthesizer, $\jest$.
  %
  We applied our tool to the latest language specification (ES13, 2022) for
  evaluation, and it automatically synthesized \inred{5,000} conformance tests
  in \inred{100} hours.
  %
  We tested \inred{eight} mainstream targets (\inred{four} engines and
  \inred{four} transpilers) with synthesized conformance tests and discovered
  bugs in all of them.
  %
  Our tool detected \inred{50} unique conformance bugs (\inred{20} in engines
  and \inred{30} in transpilers), while the baseline tool detected only
  \inred{16} engine bugs.
  %
  We had reported all detected bugs, developers confirmed all of them, and
  \inred{40} were undiscovered bugs.
  %
  \inred{Furthermore, 25 test cases detected by our tool were added to Test262,
  the official JavaScript conformance test suite.}
\end{abstract}
