\section{Conclusion}\label{sec:conclusion}

The conformance testing of programming language implementations is crucial to
support correct and consistent execution environments.
%
Graph coverage is one of the most widely-used coverage criteria in evaluating
the quality of conformance tests.
%
While graph coverage in mechanized language specifications is one of good
options as uniform coverage for multiple implementations, it does not produce
high-quality conformance tests.
%
To resolve this problem, this paper introduce \textit{feature-sensitive (FS)
coverage} as a novel coverage criterion to generate high-quality conformance
tests.
%
The core idea is refining conventional test requirements using the innermost
enclosing language features.
%
We also present \textit{feature-call-path-sensitive (FCPS) coverage} as its
variant with feature-call-paths from language features to test requirements.
%
In addition, we extend both coverage criteria using the $k$-limiting approach as
$k$-FS coverage and $k$-FCPS coverage.
%
Finally, we experimentally show that the new coverage criteria outperform the
traditional coverage criteria in the context of conformance bug detection in
eight mainstream JavaScript implementations (four engines and four transpilers)
with the latest ECMA-262 (ES13, 2022).
%
The tool detected \inred{115} distinct conformance bugs (\inred{40} in engines
and \inred{75} in transpilers), \inred{80} of which were confirmed by the
developers and \inred{40} of which were newly discovered bugs.
